Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex

% h - deleted participants # for consistencies - P4, P6 and P10 for future reference
\subsubsection{Rewinds vs. Static Photos} 
Our study reveals that participants have higher memory of locations when presented with Rewinds than with static street-view photos, $\chi^2(1, N=356) = 96.987$, $p <.01$. When presented with a street-view photo generated from the participant's location data, participants were able to recognize the depicted location 49.7\% of the time. Recognition rate of locations reached 96.6\% when participants were shown the accompanying Rewind. As discussed above, this can be expected because cinematic media like Rewinds provide more context and retrieval cues. Three participants who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind. They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' When we evaluate Rewind memorability based on trip memory rather than location memory, the results show that participants recalled the exact trip depicted by the Rewind 53.7\% of the time.
%TODO make sure episodic memory is discussed in discussion section--visit frequency diminishes episodic memory

%TODO h - add another table, only abt memorability tho
%TODO  where is home? need to explain this part in system? make sure this is explained
\subsubsection{Distance}
% only affect location rememberance
% 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
The depicted location's distance away from the participant’s home had differing effects on photo memorability and Rewind memorability. Photo memorability and distance had a clearly linear relationship, while the relationship between Rewind memorability and distance was more nuanced.

@@

\subsubsection{Visit Frequency}
% only affect location rememberance
% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
Location memorability and trip memorability are affected differently by frequency of visits (Table~\ref{table:betweensubjects}). Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited. The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study. In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,N=128) = 14.458$, $p <.01$. This effect does not occur for trip memorability. In the most frequently visited places, trips are remembered 51\% of the time. Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%. Our study also shows that comparing to static street-view images, recollection of trip memories using Rewinds is significantly improved for least frequently taken trips by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.

% Our study examined episodic processing in metric-specific groups, as well as the performance overall. Our study shows that comparing to static street-view images, recollection of event-driven memories using Rewinds is significantly improved for trips taken that were 100 - 1,000 km (62 - 620 miles) away from home by 50\%, $\chi^2(1, N=20) = 3.215$, $p <.05$; and for trips that were least frequently taken by about 20\%, $\chi^2(1, N=161) = 5.977$, $p <.01$.

>>>>

% h - deleted participants # for consistencies - P4, P6 and P10 for future reference
\subsubsection{Rewinds vs. Static Photos} 
Our study reveals that participants have higher semantic memory of locations when presented with Rewinds than with static street-view photos ($\chi^2(1, N=356) = 96.987$, $p <.01$). When presented with a street-view photo generated from the participant's location data, participants were able to recognize the depicted location 49.7\% of the time. Recognition rate of locations reached 96.6\% when participants were shown the accompanying Rewind. As discussed above, this can be expected because cinematic media like Rewinds provide more context and retrieval cues. Three participants (P4, P6, and P10) who were unable to recall a location from a static photo actually recognized the location after seeing the accompanying Rewind. They expressed their contentment after watching the Rewind, proclaiming ``I recognize the photo now!'' Further differences between Rewinds and static photos are discussed in the following sections.
%TODO h - add another table, only abt memorability tho

\subsubsection{Distance}
%TODO  where is home? need to explain this part in system? make sure this is explained
% only affect location rememberance
% 0 - 100%, 1 - 75%, 2 - 72%, 3 - 44%, 4 - 52%, 5 - 10%, $\chi^2(5,179) = 18.106$, p < 0.01
The depicted location's distance away from the participant’s home had differing effects on photo memorability and Rewind memorability. Photo memorability and distance had a clearly linear relationship, while the relationship between Rewind memorability and distance was more nuanced.

@@

When comparing photo memorability and Rewind memorability based on distance, our study shows that for trips close to home (Distance Group 1), photo remembrance was higher by 50\%, $\chi^2(1, 16) = 2.25$, $p = 0.067$. For trips far from home (Distance Group 5), Rewind remembrance was higher by 50\%, $\chi^2(1, 20) = 3.516$, $p < 0.05$. This suggests that the suitability of photos or Rewinds as memory media may differ depending on how far away from home a person is when they want to document a location. %TODO expand on this in discussion

\subsubsection{Visit Frequency}
% only affect location rememberance
% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
Differences in photo memorability due to visit frequency were statistically significant, while differences in location memorability were not. Photo memorability is higher for locations that are most frequently visited by the participant, with a remembrance rate of 72.3\%. Photo remembrance rate for the least frequently visited locations is 35.8\%. This is statistically significant at $\chi^2(1,128) = 14.458$, $p < 0.01$.

Between photos and Rewinds, photos had a higher remembrance rate for most frequently visited locations, with a difference of 20.2\% $\chi^2(1, N=20) = 3.215$, $p <.05$; and for least frequently visited locations Rewinds had a higher remembrance rate with a difference of 20.5\%, $\chi^2(1, N=161) = 5.977$, $p <.01$, suggesting again that photos and Rewinds may have different suitabilities as memory media.
